Spatial Reasoning and Statistical Graphics

### 2014-10-11 Paper/Draft1/TestingVisualAptitude.Rnw
Visual Search discussion

In figure~\ref{fig:visualaptitudects}, we see that participant performance on lineups is positively correlated with performance on card rotation, figure classification, and paper folding tasks. This suggests that skills associated with visual reasoning ability are related to lineup performance. As participants must use the same skills in lineups (mental rotation, classification and determining categorization schemes, and multi-step spatial reasoning) as in the factor-referenced tests, this is not particularly surprising. 
\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{fig-VisReasoningAnalysisCat}
\caption[Visual Aptitude Study Results]{Preliminary results of categorical variables compared to lineup score.}\label{fig:visualaptitudecat}
\end{figure}

>>>>

In figure~\ref{fig:visualaptitudects}, we see that participant performance on lineups is positively correlated with performance on card rotation, figure classification, and paper folding tasks. This suggests that skills associated with visual reasoning ability are related to lineup performance. As participants must use the same skills in lineups (mental rotation, classification and determining categorization schemes, and multi-step spatial reasoning) as in the factor-referenced tests, this is not particularly surprising. In addition,there seems to be some positive relationship between a participant's score on the visual search task and their score on lineups: the visual search task represents a baseline of a participant's ability to find a matching pattern, while lineups require that task as well as the ability to determine what the pattern is for a particular graph. Even excluding the one low visual search score that is a high-leverage point, there seems to be a positive relationship between a participant's score on lineups and their score for visual search.

\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{fig-VisReasoningAnalysisCat}
\caption[Visual Aptitude Study Results]{Preliminary results of categorical variables compared to lineup score.}\label{fig:visualaptitudecat}
\end{figure}
